TBD

### 2021-02-25 outputs/paper/paper.Rmd
Edit captions of figures

# Round values
t_tests[] <- lapply(t_tests, round, 2)

@@

### Chi-squared test
q7_chi <- table(all_simulated_dataset$Q7, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared Test for Q7", q7_chi$statistic, q7_chi$parameter, q7_chi$p.value)
```

@@

### Chi-squared test
q8_chi <- table(all_simulated_dataset$Q8, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared Test for Q8", q8_chi$statistic, q8_chi$parameter, q8_chi$p.value)
```

@@

### Chi-squared test
q10_chi <- table(all_simulated_dataset$Q10, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared Test for Q10", q10_chi$statistic, q10_chi$parameter, q10_chi$p.value)
```

>>>>

# Round values
t_tests[] <- lapply(t_tests, round, 3)

@@

### Chi-squared test
q7_chi <- table(all_simulated_dataset$Q7, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared test to examine the possibility of an association between the intervention and the total sales", q7_chi$statistic, q7_chi$parameter, q7_chi$p.value)
```

@@

### Chi-squared test
q8_chi <- table(all_simulated_dataset$Q8, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared test to examine the relation between the intervention and the total sales and a decline in revenue", q8_chi$statistic, q8_chi$parameter, q8_chi$p.value)
```

@@

### Chi-squared test
q11_chi <- table(all_simulated_dataset$Q11, all_simulated_dataset$type) %>%
  chisq.test()
tableChisq("Pearson's Chi-squared test to examine the association of the intervention with price adjustments", q11_chi$statistic, q11_chi$parameter, q11_chi$p.value)
```
